Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Community Detection and Parameter Estimation

### 2021-04-20 summary.Rmd
updated theorem 5

@@

$$L_c(\hat{\sigma}, \sigma; \{v_i\}) = 
\min_\pi \sum_i I(\pi \circ \hat{\sigma}(v_i) = \sigma{v_i})$$

where $\sigma(v_i)$ is the true community label of vertex $v_i$, 
$\hat{\sigma}(v_i)$ is a community assignment function, and $\pi$ is a 
permutation operator. This is effectively the "misclustering count" of
$\hat{\sigma}$.

We then define parameter estimation error as the MSE up to sign flip:

$$MSE(\{\hat{\lambda}^{(kl)}\}, \{\lambda^{(kl)}\}) = 
\min_{s \in \{-1, 1\}} 
\sqrt{\frac{1}{n} \sum_{k < l} \sum_{i = 1}^{n_k} 
(s \hat{\lambda}^{(kl)}_i - \lambda^{(kl)}_i)^2}$$

@@

Let $V_{n, -i}^{(k)}$ be $V_n^{(k)}$ with the $i$^th^ entry removed. Suppose 
that for each community $k$, there are enough vertices such that for each $i$, 
$V_{n, -i}^{(k)}$ spans its corresponding subspace (Theorem 2). 
Then $r_n^{(k)} = \min\limits_i r(V_{n, -i}^{(k)}) > 0$. 
Thus by (\ref{eq:mu-conv}), for each $k$, $r_n^{(k)} > \mu_n^{(k)}$ where 
$\mu_n^{(k)} = \mu(\hat{V}_n^{(k)})$ and $n$ is large enough such that 
$\min\limits_{k, i} rank(V_{n, -i}^{(k)}) = K$.

Let $r_n = \min_k r_n^{(k)}$. By (\ref{eq:delta-conv}), 
$\delta_n \stackrel{a.s.}{\to} 0$. Then as $n\to \infty$, 
$\delta_n < \min_k \frac{r_n (r_n^{(k)} - \mu_n^{(k)})}{2 + 7 r_n^{(k)}}$ 
with probability 1.

@@

>>>>

\begin{remark}
The proof of Theorem \ref{theorem5} is a direct consequence of Theorem 6 
from  \citeauthor{jmlr-v28-wang13} and the fact that the unscaled ASE of 
$P_n$ consists of orthogonal subspaces. \citeauthor{jmlr-v28-wang13} assume 
that the points in the embedding are all of unit length, and while we apply 
this normalization in the simulated examples, it is not strictly necessary 
for Theorem \ref{theorem5} due to orthogonality. 
\end{remark}

@@

$$L_c(\hat{\sigma}, \sigma; \{v_i\}) = 
\min_\pi \sum_i I(\pi \circ \hat{\sigma}(v_i) = \sigma(v_i))$$

where $\sigma(v_i)$ is the true community label of vertex $v_i$, 
$\hat{\sigma}(v_i)$ is the predicted label of $v_i$, and $\pi$ is a 
permutation operator. This is effectively the "misclustering count" of
clustering function $\hat{\sigma}$.

We also define parameter estimation error as the RMSE up to sign flip:

$$RMSE(\{\hat{\lambda}^{(kl)}\}, \{\lambda^{(kl)}\}) = 
\sqrt{\frac{1}{n} \sum_{k < l} \min_{s \in \{-1, 1\}} 
\sum_{i = 1}^{n_k} 
(s \hat{\lambda}^{(kl)}_i - \lambda^{(kl)}_i)^2}$$

@@

Let $V_{n, -i}^{(k)}$ be $V_n^{(k)}$ with the $i$^th^ entry removed. Suppose 
that for each community $k$, there are enough vertices such that for each $i$, 
$V_{n, -i}^{(k)}$ spans its corresponding subspace (Theorem \ref{theorem2}). 
Then $r_n^{(k)} = \min\limits_i r(V_{n, -i}^{(k)}) > 0$. 
Thus by (\ref{eq:mu-conv}), for each $k$, $r_n^{(k)} > \mu_n^{(k)} = 0$ where 
$\mu_n^{(k)} = \mu(\hat{V}_n^{(k)})$ and $n$ is large enough such that 
$\min\limits_{k, i} \text{rank}(V_{n, -i}^{(k)}) = K$.

Let $r_n = \min\limits_k r_n^{(k)}$. By (\ref{eq:delta-conv}), 
$\delta_n \stackrel{a.s.}{\to} 0$. Then as $n\to \infty$, 
$\delta_n < \min\limits_k 
\frac{r_n (r_n^{(k)} - \mu_n^{(k)})}{2 + 7 r_n^{(k)}}$ 
$= \min\limits_k \frac{r_n r_n^{(k)}}{2 + 7 r_n^{(k)}}$
with probability 1.

@@

\begin{remark}
Theorem 6 of \citeauthor{jmlr-v28-wang13} assume that each $||v_n^{(i)}|| = 1$, 
which scales each $r_n^{(k)} \leq 1$. This is not strictly necessary for 
the proof of Theorem \ref{theorem5} since each $\mu_n^{(k)} = 0$, so as long 
as the $k^{th}$ community spans its subspace, $r_n^{(k)} > 0 = \mu_n^{(k)}$.
\end{remark}
